---
title: "R Notebook"
output: html_notebook
Author: Deexith Reddy
Date: 12/02/2020
---



```{r}
#PROBLEM 1
## PROBLEM 1A

#When we say A and B are independent events, this implies that event A does not have an impact on outcome of event B. 
#Similarily, the probabilitiy of event A happening has no impact on probability of event B happening. Correlating the same, the probabilitiy of event A happening will not have an impact on event B not happening.

## PROBLEM 1B
A) 1/4 or 0.25 
B) 0              #Mutually exclusive
C)1/4 or 0.25
D)0               #Mutually exclusive
E)13/20 or 0.65   #P(AUB) = P(A) + P(B) - P(AnB), P(AnB) = 0
F)2/5 or 0.4      #P(AUB) = P(A) + P(B) - P(AnB), P(AnB) = 0.25
G)5/8 or 0.625    #P(AnB) = 0.25
H)0               #P(AnB) = 0, Mutually Exclusive



```



```{r}
#PROBLEM 2
## PROBLEM 2A
P(A) = 1/2 or 0.5             #PROBABLITY THAT STOCK OUTPERFORMS

## PROBLEM 2B

P(A) = 0.5  #PROBABLITY STOCK OUTPERFORMS
P(B) = 0.5  #PROBABLITY STOCK UNDERPERFORMS

#P(C) is probablity that the software is correct
#P(C') is probablity that the software predicts incorrect

P(c|A) = 0.63 #PROBABLITY SOFTWARE PREDICTS CORRECTLY GIVEN STOCK OUTPERFORMS
P(c|B) = 0.61 #PROBABLITY SOFTWARE PREDICTS CORRECTLY GIVEN STOCK UNDERPERFORMS


#When software predicts that market outperforms and predicts incorrectly is same as the market actually underperformed.So we are given that market underperformed.

#Probablity that the software predicts incorrectly given that market underperformed = P(C'|B)

P(C'|B) = 1-P(c|B) = 1-0.61 = 0.39

## PROBLEM 2C
#Let Z be the amount of money invested
#When the market outperforms then the profit will be = (12/100)*Z
#When the market underperforms then the profit will be = (2/100)*Z

#P(C) is probablity that the software is correct
#P(C') is probablity that the software predicts incorrect

#When market underperforms:
#Probablity of the software predicting correct and market outperformed along with incorrect and underperformed:
= P(CnA) U P(C'nB)
= P(c/A)P(A) u P(C'/B)P(B)
=(0.63/2 + 0.39/2)=0.51
#Weighted average of outperform component: (12/100)*Z*0.51

#When market underperforms:
#Probablity of the software predicting incorrect and market outperformed along with correct and underperformed: 
=P(C'nA) U P(CnB)
= P(c'/A)P(A) u P(C/B)P(B)
= (0.37/2 + 0.61/2)=0.49
#Weighted average of underperform component: (2/100)*Z*0.49

#Therefore the equation will be:
  
#(12/100)*Z*0.51 + (2/100)*Z*0.49 > 150,000

#Therefore z= $ 2,112,676.06

## PROBLEM 3D

#To invest in each stock, we need to divide the the total amount to be invested by 10. SO we invest $ 212,676.06 in each stock.

```


```{r}
#PROBLEM 3
## PROBLEM 3A
1/2 or 0.5

## PROBLEM 3B

#Let x be investment successful in 1st attempt
#Let y be investment successful in 2nd attempt
#Let z be investment successful in 3rd attempt
#Let P(xnynz) be probability of investments being successful
#Let P(x'ny'nz') be probability of investments not being successful
#x',y',z' are considered not successful investments

 P(z | (xnynz) u (x'ny'nz')) = 
     P(z n [(xnynz) u (x'ny'nz')]) /  P((xnynz) u (x'ny'nz'))

 Here,  
 P(z) n P(x'ny'nz') = 0
 P(z) n P(xnynz) = P(xnynz)
     
   = P (xnynz)/ (P((xnynz) + (x'ny'nz'))
   = (1/8)/(2/8)
   = 1/2
 
 ## PROBLEM 3C
 
 P(z | (xnynz') u (xny'nz) u (x'nynz) )
 
= P(z n ((xnynz') u (xny'nz) u (x'nynz)))/P((xnynz') u (xny'nz) u (x'nynz))

Here, 
 P(z) n P(x'ny'nz') = 0
 P(z) n P(xny'nz) = 1/8
 P(z) n P(x'nynz) = 1/8
 P((xnynz') u (xny'nz) u (x'nynz)) = ((1/8)+(1/8)+(1/8))=3/8
 THerefore
 
  P(z | (xnynz') u (xny'nz) u (x'nynz) ) = ((1/8)+(1/8))/(3/8)=2/3
 
 ## PROBLEM 3d
 
 #For two independent events z and x: P(znx)=P(z) * P(x)
 
 #LET TWO SUCESSFUL INVESTMENTS = A
 #Let x be investment successful in 1st attempt
#Let y be investment successful in 2nd attempt
#Let z be investment successful in 3rd attempt
#x',y',z' are considered not successful investments
 
 P(A) = P(xnynB') + P(x'nynB) + P(xny'nB)
      = (0.845*0.5505*0.6) + (0.155*0.5505*0.4) + (0.845*0.4495*0.4)
      = 0.40
 P(B) is Third event being successful
 
 Since, P(A) includes the third investment being successful, these are dependent events.
      
 


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
