---
title: "HOMEWORK 2 SOLUTION"
output: html_notebook
author: DEEXITH REDDY
---



```
```{r}
data("women")
help("women")
install.packages("moments")
```
#Problem 1

## Problem 1 a
#There are two variables in this data frame. Each variable represents numeric	Height in inches (in) and numeric	Weight in pounds (lbs).

##Problem 1 b

```{r}
BMI <- (women[,2]*703)/(women[,1]**2)                   #CALCULATING BMI
print(BMI)

```

## Problem 1 c
```{r}
women$BODY_MASS_INDEX <-BMI                 #CREATING COLUMN "BODY_MASS_INDEX:                                              HAVING BMI 
print(women)

```

## Problem 1 d
```{r}
ARITHMETIC_MEAN <- sum(BMI)/length(BMI)                     #CALCULATING MEAN
print(ARITHMETIC_MEAN)

SAMPLE_STDEV <- ((sum((women[,3]-ARITHMETIC_MEAN)**2))/(length(BMI)-1))**0.5 
print(SAMPLE_STDEV)

SAMPLE_SKEWNESS <-((sum((women[,3]-ARITHMETIC_MEAN)**3))/(length(BMI)))/((sum((women[,3]-ARITHMETIC_MEAN)**2))/(length(BMI)-1))**1.5
print(SAMPLE_SKEWNESS)

SAMPLE_KURTOSIS <-((sum((women[,3]-ARITHMETIC_MEAN)**4))/(length(BMI)))/((sum((women[,3]-ARITHMETIC_MEAN)**2))/(length(BMI)))**2
print(SAMPLE_KURTOSIS)


## Problem 1 e
##The BMI is skewed. As we plot a Histogram of BMI, it is right skewed. We have a frequency of 8 between BMI 22.0 and 22. The remaining frequencies are distributed between 22.5 and 24.5, showing the skew.

## Problem 1 f
##The distribution is playtkurtic since the Kurtosis is 2.35 or less than 3. There are only two outliers after BMI of 23.5.


# Problem 2

##Problem 2 a
library(readxl)
filtered_qb <- read_excel("C:/Users/DEEXITH REDDY/Downloads/filtered_qb.xlsx")
View(filtered_qb)

##Problem 2 b
#PROJECTION:
AVG_PROJECTION <- mean(filtered_qb$projections)          #CALCULATING AVERAGE
print(AVG_PROJECTION)

STANDARD_DEVIATION <- sd(filtered_qb$projections)       #CALCULATING STANDARD                                                           DEVIATION
print(STANDARD_DEVIATION)

install.packages("moments")
library(moments)
SKEWNESS_PROJECTION <- skewness(filtered_qb$projections)     #CALCULATING                                                                   SKEWNESS
print(SKEWNESS_PROJECTION)

#Actuals:
AVG_ACTUALS <- mean(filtered_qb$actuals)                   #CALCULATING AVERAGE
print(AVG_ACTUALS)

STANDARD_DEV_ACTUALS <- sd(filtered_qb$actuals)            #CALCULATING STANDARD                                                           DEVIATION
print(STANDARD_DEV_ACTUALS)

library(moments)
SKEWNESS_ACTUALS <- skewness(filtered_qb$actuals)          #CALCULATING                                                                   SKEWNESS
print(SKEWNESS_ACTUALS)

hist(filtered_qb$projections)
hist(filtered_qb$actuals)

#CENTRAL TENDENCY
#The standard deviation for projections is 2.37 while for actuals is 9.01. This shows that for central tendency is more for projections while it is low for actuals.

#VARIABILITY:
# The standard deviation for projections is 2.37 while for actuals is 9.01. This shows that for actuals,variability is high while for projections it is low when compared to mean.

#SHAPE:
#While the distribution of projections is right skewed, the distribution of actuals is skewed on two sides. This is also showed by skewness number of projections which is 1.00 and skewness of actuals is 0.42.

##Problem 2 c
our.five.sum <- fivenum(filtered_qb$actuals)    #USING FIVENUM FUNCTION
print(our.five.sum[3])                          #PRINTING MEDIAN

##Problem 2 d
boxplot(filtered_qb$actuals)                    #BOXPLOT GENERATION
boxplot(filtered_qb$projections)                #BOXPLOT GENERATION

plot(filtered_qb$actuals,filtered_qb$projections, pch=19, col=c("red","blue"))
#The plot is fairly accurate. It shows that actuals is spread over the chart, i.e, the spread and deviation from mean is more(red colour).While for projections,deviation and spread is less since the points are around the mean(blue colour).

hist(filtered_qb$actuals)                         #HISTOGRAPH GENERATION
hist(filtered_qb$projections)                     #HISTOGRAPH GENRATION

hist(filtered_qb$actuals, breaks = 10)            #HISTOGRAPH WITH BREAKS = 10
hist(filtered_qb$actuals, breaks = 30)            #HISTOGRAPH WITH BREAKS = 30 

# Problem 3

##Problem 3 a

random <- rnorm(n=4, mean=0, sd=10)                  #RANDOM SET GENERATION
print(random)

##Problem 3 b 
s = ((sum((random[])**2))/(length(random)-1))**0.5  #SAMPLE STANDARD DEVIATION
print(s)                                            # MEAN = 0, not included

##Problem 3 c
s = ((sum((random[])**2))/(length(random)))**0.5   #POPULATION STANDARD                                                           DEVIATION
print(s)                                           # MEAN = 0, not included

## PROBLEM 3 d

record <- list(matrix(nrow = 10, ncol = 6,byrow = TRUE)     #MATRIX TO STORE     
dimnames(record) = list(c(R1,R2,R3,R4,s1,s2))                      

for (a in 1:10)                               #FOR LOOP FOR GENRATING 10 SETS
{
list1 <- c(rnorm(n=4, mean=0, sd=10))        #VARIABLE FOR RANDOM NUMBER SET
print(list1)
 
s1 <- c(((sum((list1)**2))/(length(list1)-1))**0.5)    #SAMPLE STANDARD                                                               DEVIATION
print(s1)                                             # MEAN = 0, not included

s2 <- c(((sum((list1)**2))/(length(list1)))**0.5)         #POPULATION STANDARD                                                            DEVIATION
print(s2)                                           #MEAN = 0, not included
 
list1 <- c(list1, s1, s2)
 
record[a,] <- c(list1)

}

print(record)

## PROBLEM 3 e

#The sample standard deviation is closer to the 10 whenever both, population and sample standard deviations go above 10. When both the standard deviations are below 10, the population standard deviation is closer. When the population standard deviation is more than 10 and sample standard deviation is lesser than 10, then sample standard deviation is closer to 10. Hence, in all cases the factor of (n-1) in denominator is weighing in and causes sample standard deviation closer to 10.

