---
title: "R Notebook"
output: html_notebook
---
```{r}
#ANSWER 1
##ANSWER 1 A
# The probability of task being completed in 17 minutes or more is equal to 1 minus probability of task being completed in less than or equal to 16 minutes.
#P(X>=17)=1-P(x<=16)  #X is no. of minutes

q=17
a<-punif(q, min = 10, max = 25, lower.tail = TRUE, log.p = FALSE)
z=1-a
print(z)

```
```{r}
##ANSWER 1 B
# The probability of task being completed in after seventeen minutes given that it was completed in twenty minutes:
#P(x>=17|20)=(P(X>=17)nP(X>=20))/P(x>=20)          #WE CONSIDER MAXIMUM AS 20, MINIMUM AS 10         #X is no. of minutes
#            =(20-17)/(20-10)
#            =3/10
a<-20
t<-17
b<-10
P<-(a-t)/(a-b)
print(P)


```

```{r}
##ANSWER 1 C
#MEAN = (a+b)/2=20  #b is maximum, a is minimum
#VARIANCE=((b-a)^2)/12=18.75
# We find a and b using linear algebra equations:

#(a+b)=40
#(b-a)=15 
#2b=55 
#b=27.5 
#a=12.5 
#MAXIMUM = 27.5
#MINIMUM = 12.5
```


```{r}
#ANSWER 2
##ANSWER 2A
#Expected arrivals: (ARRIVALS/MINUTE)* NO. OF MINUTES
#A=ARRIVALS/MINUTE
#B=NO. OF MINUTES
#E=EXPECTED VEHICLES

A=7
B=30
E=A*B
print(E)  #210
```


```{r}
##ANSWER 2B
#Expected arrivals: (ARRIVALS/MINUTE)* NO. OF MINUTES
#A=ARRIVALS/MINUTE
#B=NO. OF MINUTES
#E=EXPECTED VEHICLES

A=4
B=30
E=A*B
print(E)  #120
```
```{r}
##ANSWER 2C
#z=P(X>19) = 1 - P (X<=19)            #X is no. of cars
q=19  #No. pf cars for which probabilty is to be calculated
a=7 #Cars per minute
b=3 #Interval time
l= a*b #Cars in that interval
z<-1-ppois(q,l, lower.tail = TRUE, log.p = FALSE)
print(z)    #ANSWER=0.6157372
```


```{r}
##ANSWER 2d
#z=P(T=4)*P(C<12)=P(T=4)*P(C<=11),  #T is no. of trucks, C is no. of cars

t<-4  #No. of trucks for which probabilty is to be calculated
c<-4 #Trucks per minute
d<-2 #Interval time
f<-c*d
p<-dpois(t,f,log = FALSE)

q=11  #No. of cars for which probabilty is to be calculated
a=7 #Cars per minute
b=2 #Interval time
l= a*b #Cars in that interval
m<-ppois(q,l, lower.tail = TRUE, log.p = FALSE)
z<-p*m
print(z)    #ANSWER=0.01488

```
```{r}
##ANSWER 2e
a<-dpois(1:39,21)
b<-dpois(1:39,12)
c<-rev(b)
P<-sum(a*c)
print(P)
```

```{r}
##ANSWER 2f

a=7 #Cars per minute
b=4 #Trucks per minute
t=3 #Time
z=(a+b)*t #Lambda=Mean=Expected
s=z^(1/2) #STANDARD DEVIATION: (LAMBDA)^1/2
print(s) #ANSWER=5.744
    
```
```{r}
#ANSWER 3
##ANSWER 3A
#P(X>4) = 1 - P(X<=4)
#       = 1 - ppois(q,Lambda,lower.tail=True,log.p=False)

a=1/2 #AVERAGE PER HOUR
b=8   #TIME PERIOD
e=a*b #LAMBDA OR EXPECTATION
q=4  
z<-1-(ppois(q,e,lower.tail=TRUE,log.p=FALSE))
print(z) #ANSWER=0.3711631



```


```{r}
##ANSWER 3B
#The following occurs when a computer crashes:One mandatory program being affected and the remaining following binomial distribution. Hence, we subtract 1 from the selection of events. 

#If x is the crash number occuring, then:

#Probablity mass function:P(X=x)= dbinom(x-1,4,0.5,log=FALSE) if x=2,3,4,5
#                         P(X=1)=1
```


```{r}

##ANSWER 3C
#Expected programs in 1 crash: (1 + np), n=4, p=0.5
#Expected programs in 1 day: (8*(1/2))*(1+(4*0.5))

n=4
p=0.5
E<-(1+(n*p))*(4)
print(E)
```



```{r}

##ANSWER 3D
#Expectation of computer crashing in 5 day, eight hour period: (5*8*(1/2))= 20
#Expectation of program being afffected: (1 + np):(1+(4*0.5))= 3
#Probablity of computer crashing in certain 'n' minutes: x
#To find out n: qnorm(x,30,10,lower.tail=TRUE,log.p=FALSE)
# Therefore, amount of money to that could be charged:
c<-150*qnorm(x,30,10,lower.tail=TRUE,log.p=FALSE)*(5*(1/2)*8)*(1+(4*0.5))    
#TOTAL AMOUNT=RATE*Number of minutes*Expectation of computer crashing*Expectation of program affecting)

```

```{r}
##ANSWER 3E
z<-qnorm(0.25, mean = 30, sd = 10, lower.tail = TRUE, log.p = FALSE) 
print(z)

```










Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
